Gaussian Processes Autoregressive Models for the Disturbance Storm Time Index

### 2016-04-22 swsc.tex
Updates from ShareLaTeX

@@

\begin{comment}
%%
%%
%%
\begin{table}
      \caption[]{Opacity sources.}
         \label{KapSou}
     $$ 
         \begin{array}{p{0.5\linewidth}l}
            \hline
            \noalign{\smallskip}
            Source      &  T / {[\mathrm{K}]} \\
            \noalign{\smallskip}
            \hline
            \noalign{\smallskip}
            \citet{Ji2012} & \leq 1700^{\mathrm{a}}     \\
            \citet{kocijan2015modelling}                     & 1700 \leq T \leq 5000 \\
            \citet{Berlinet2004}                  & 5000 \leq             \\
            \noalign{\smallskip}
            \hline
         \end{array}
     $$ 
\begin{list}{}{}
\item[$^{\mathrm{a}}$] This is footnote a
\end{list}
\end{table}
%%
%%
%%
\end{comment}

>>>>

Before performance bench marks for \emph{OSA} $D_{st}$ prediction are run on the 63 geomagnetic storm events from 1998-2006 in \cite{Ji2012}, training and model selection of \emph{GP-AR} and \emph{GP-ARX} models on independent data sets must be performed. For this purpose we choose segments 00:00 1 January 2008 - 10:00 11 January 2008 and 00:00 15 November 2014 - 23:00 1 December 2014 for training and model selection respectively.

The time lags chosen for \emph{GP-AR} are $p = 6$ while for \emph{GP-ARX} $p=6$, $p_{ex} = 1$ are arrived by experimenting with values starting from one and choosing the value of $p$ yielding best performance on the 63 events in the bench mark.

@@

\subsection{Models Compared}

\begin{table}
      \caption[]{One Step Ahead $D_{st}$ prediction models}
         \label{table:DstModels}

         \begin{tabular}{lll}
            \hline
            \noalign{\smallskip}
            Model     &  Reference & Description \\
            \noalign{\smallskip}
            \hline
            \noalign{\smallskip}
            TL & \citet{JGRA:JGRA16300} & Auto regressive model decomposable into additive terms.      \\
            NM & \citet{balikhin:narmax} & Non linear auto regressive with exogenous inputs. \\
            B & \citet{JGR:JGR10260} & Prediction of $D_{st}$ by solving ODE having injection and decay terms. \\
            W & \citet{Wang:Dst} & Obtained by modification of injection term in \citet{JGR:JGR10260}. \\
            FL & \citet{GRL:GRL11549} & Uses polarity of magnetic clouds to predict geomagnetic response.\\
            OM & \citet{JGRA:JGRA14856} & Modification of injection term in \citet{JGR:JGR10260}.\\
            \noalign{\smallskip}
            \hline
         \end{tabular}
\end{table}
